\begin{thebibliography}{9}
    \bibitem{PAPS}
        Baresi, L., Mendonça, D., Quattrocchi, G.: 
        \textit{PAPS: A Framework for Decentralized Self-management at the Edge.}
        In: Service-Oriented Computing, pp.508-522, (2019).   

    \bibitem{SLPA}
        Xie, J., Szymanski, B K, Liu, X.:
        \textit{SLPA: Uncovering Overlapping Communities in Social Networks via
        A Speaker-listener Interaction Dynamic Process.}
        In Proc: Data Mining Technologies for Computational Collective 
        Intelligence Workshop at ICDM, Vancouver, CA pp. 344-349, (2011)

    \bibitem{Edge}
        Wang R, Yan J, Wu D,:
        \textit{Edge Computing: Applications, State-of-the-Art and Challenges, Advances in Networks.}
        Vol. 7, No. 1, pp. 8-15. doi: 10.11648/j.net.20190701.12 (2019)

    \bibitem{Edge2}
        Shufen Wang:
        \textit{Knowledge-Centric Edge Computing Based on Virtualized D2D Communication Systems.}
        IEEE Communications Magazine, 56 (5): 32-38. (2018)

    \bibitem{DataGrowth}
        Zhang Yanjun, Yang Xiaodong, Liu Yi, Zheng Dayuan, Bi Shujun:
        \textit{Research on the Frame of Intelligent Inspection Platform Based on Spatio-temporal Data.}
        Computer \& Digital Engineering, 47 (03): 616-619+637. (2019)

    \bibitem{IoT}
        Y. Wu, Y. Liu, S. H. Ahmed, J. Peng, A. A. A. El-Latif,
        \textit{“Dominant dataset selection algorithms for electricity consumption time-series data analysis based on affine transformation}
        IEEE Internet of Things Journal, pp. 1–1. (2019)

    \bibitem{EnEff}
    1   Satyanarayanan M.:
        \textit{The Emergence of Edge Computing.}
        Computer, 50 (1): 30-39. (2017)
    
    \bibitem{Edge4}
        Tuyen Xuan Tran, Pompili D.:
        \textit{Joint Task Offloading and Resource Allocation for Multi-Server Mobile-Edge Computing Networks} PP (99): 1-1. (2017)

    \bibitem{Edge5}
        Feng W, Jie X, Xin W.:
        \textit{Joint Offloading and Computing Optimization in Wireless Powered Mobile-Edge Computing Systems.} 
        IEEE Transactions on Wireless Communications, PP (99): 1-1. (2017)

    \bibitem{Communication}
        Mao Y, Zhang J, Song S H.:
        \textit{Stochastic Joint Radio and Computational Resource Management for Multi-User Mobile-Edge Computing Systems.} 
        IEEE Transactions on Wireless Communications, 16 (9): 5994-6009. (2017)

    \bibitem{MEC1}
        Mach, P., Becvar, Z.:
        \textit{Mobile edge computing: A survey on architecture and computation offloading.}
        IEEE Comm. Surveys and Tutorials 19(3), 1628–1656 (2017)

    \bibitem{MEC2}
        Several authors:
        \textit{Mobile edge computing (mec); framework and reference architecture.}
        Tech. rep., ETSI GS MEC (01 2019), \\
        http://www.etsi.org/deliver/etsi\_gs/MEC/001\_099/003/01.01.01\_60/gs\_MEC003v010101p.pdf

    \bibitem{Serverless}
        Gadepalli P.K., Peach G., Cherkasova L., Aitken R., Parmer G.:
        \textit{Challenges and Opportunities for EfficientServerless Computing at the Edge.}
        pp. 1. (2019)

    \bibitem{Containers}
        Pahl C., Brogi A., Soldani J., Jamshidi P.:
        \textit{Cloud Container Technologies: a State-of-the-Art Review.}
        IEEE Transactions on Cloud Computing. PP. 1-1. (2017). 

\end{thebibliography}